### 2019-07-09 monograph/thesis/chapters/beautifiers.tex
Wrapped \lang English text accordingly to semantic line wrap rules
Finished the translation of the last citation from beautifiers.tex

\lang{%
    For now could not find any strong evidence or correlation about code
    comprehension and source code beautifying \cite{improvingCodeReadability},
    except perhaps for team annoyance:
}{%
    Não pôde~=se encontrar nenhuma forte evidência ou
    relação sobre a compreensão de códigos~=fonte e
    formatadores de código.
    Somente indícios de que certas características combinadas podem melhorar ou
    facilitar a tarefa de programar \cite{pep8operatorsBlankLine}.
}%
\begin{citacao}
    % \setlength{\itemindent}{5pt}
    Um dos melhores métodos de destruição de equipes de desenvolvedores de software,
    é engajar~=se em guerras de formatação passiva~=agressiva.
    Eles destroem os relacionamentos entre colegas,
    e dependendo do tipo de formatação feita,
    também podem prejudicar a capacidade de comparar efetivamente as revisões no sistema de controle de versão,
    o que é realmente assustador.
    Não pode~=se nem imaginar o quão ruim seria caso a liderança das equipes fosse a culpada por esse comportamento.
    Isso é liderar por exemplo.
    Por mau exemplo.
    \cite[tradução nossa]{deathToTheSpaceInfidels}\footnote{
    \englishword{%
    One of absolute worst,
    worst methods of teamicide for software developers is to engage in these kinds of passive~=aggressive formatting wars.
    I know because I've been there.
    They destroy peer relationships,
    and depending on the type of formatting,
    can also damage your ability to effectively compare revisions in source control,
    which is really scary.
    I can't even imagine how bad it would get if the lead was guilty of this behavior.
    That's leading by example,
    all right.
    Bad example.
    }}.
\end{citacao}

\lang{%
    On \citeonline{improvingCodeReadability} was analyzed the level of program comprehension which can be gained by the indentation and
    was constated that the indentation levels of 2 and
    4 spaces proved to have the best comprehension levels again other levels.
}{%

}
\begin{citacao}
So yes, absurd as it may sound, fighting over whitespace characters and other seemingly
trivial issues of code layout is actually justified. Within reason of course -- when done
openly, in a fair and concensus building way, and without stabbing your teammates in the
face along the way. \cite{deathToTheSpaceInfidels}
\end{citacao}

@@

\citeonline{annotationAssistant},
\citeonline{codePlagiarismDetection},
\citeonline{softwarePortfolio},
\citeonline{legacyAssets},
\citeonline{massMaintenance},
\citeonline{prettyPrinting},
\citeonline{architectureFormatting},
\citeonline{independentFramework},
\citeonline{programIndentation},
\citeonline{industrialApplication},
\citeonline{toolsForProjectManagement},
\citeonline{codeClassification},
\citeonline{codeScanningPatterns},
\citeonline{debuggingIntoExamples},
\citeonline{programUnderstanding},
\citeonline{documentingAndSharingKnowledge},
\citeonline{autofoldingForSourceCode},
\citeonline{learningSupportSystem},
\citeonline{syntaxHighlightingInfluencing},
\citeonline{improvingCodeReadability},
\citeonline{howNovicesRead},
\citeonline{theRoleOfMethodChains},
\citeonline{codeComprehensionComparedToOO},
\citeonline{enhancingLegacySoftwareSystemAnalysis},
\citeonline{moldableCodeEditor},
\citeonline{blindAndSightedProgrammers},
\citeonline{pushdownAutomata},

>>>>

\lang{%
    For now could not find any strong evidence or
    correlation about code comprehension and
    source code beautifying \cite{improvingCodeReadability},
    except perhaps for team annoyance:
}{%
    Não pôde~=se encontrar nenhuma forte evidência ou
    relação sobre a compreensão de códigos~=fonte e
    formatadores de código.
    Alguns estudos como \citeonline{improvingCodeReadability} implementam modelos de Inteligências Artificiais,
    utilizados para classificar trechos de código~=fonte como ``bem legíveis'' ou
    ``mal legíveis''.
    Inicialmente estes estudos começam coletando dados de pessoas,
    para então treinar Inteligências Artificiais para classificar códigos~=fonte.

    Além desses estudos científicos para classificar códigos~=fonte,
    encontra~=se em outros lugares como \citeonline{pep8operatorsBlankLine} dicas ou
    notas explicando quais características de formatação de código~=fonte ajudam ou
    prejudicam a legibilidade de código.
}%
\begin{citacao}
    % \setlength{\itemindent}{5pt}
    Um dos melhores métodos de destruição de equipes de desenvolvedores de software,
    é engajar~=se em guerras de formatação passiva~=agressiva.
    Elas destroem os relacionamentos entre colegas,
    e dependendo do tipo de formatação feita,
    também podem prejudicar a capacidade de comparar efetivamente as revisões no sistema de controle de versão,
    o que é realmente assustador.
    Não pode~=se nem imaginar o quão ruim seria caso a liderança das equipes fosse a culpada por esse comportamento.
    Isso que é liderar por exemplo.
    Por mau exemplo.
    \cite[tradução nossa]{deathToTheSpaceInfidels}\footnote{
    \englishword{%
    One of absolute worst,
    worst methods of teamicide for software developers is to engage in these kinds of passive~=aggressive formatting wars.
    I know because I've been there.
    They destroy peer relationships,
    and depending on the type of formatting,
    can also damage your ability to effectively compare revisions in source control,
    which is really scary.
    I can't even imagine how bad it would get if the lead was guilty of this behavior.
    That's leading by example,
    all right.
    Bad example.
    }}.
\end{citacao}

\lang{%
    On \citeonline{programIndentation} was analyzed the level of program comprehension which can be gained by the indentation and
    was comprehended that the indentation levels of 2 and
    4 spaces proved to have the best comprehension levels again other levels.
}{%
    Em \citeonline{programIndentation} foi analisado o nível de compreensão do programa que pode ser obtido pela indentação e
    foi constatado que os níveis de indentação de 2 e
    4 espaços provaram ter os melhores níveis de compreensão do que outros níveis.
}%
\begin{citacao}
    % \setlength{\itemindent}{5pt}
    Por mais absurdo que possa parecer,
    lutar sobre espaços em branco e
    outras questões aparentemente triviais de layout de código~=fonte é realmente justificado.
    Desde que feito com moderação,
    abertamente,
    de uma forma justa e
    com construção de consenso,
    sem esfaquear os seus companheiros de equipe ao longo do caminho.
    \cite[tradução nossa]{deathToTheSpaceInfidels}\footnote{
    \englishword{%
    So yes,
    absurd as it may sound,
    fighting over whitespace characters and
    other seemingly trivial issues of code layout is actually justified.
    Within reason of course -- when done openly,
    in a fair and
    concensus building way,
    and without stabbing your teammates in the face along the way.
    }}.
\end{citacao}

@@

\citeonline{annotationAssistant},
\citeonline{codePlagiarismDetection},
\citeonline{softwarePortfolio},
\citeonline{legacyAssets},
\citeonline{massMaintenance},
\citeonline{prettyPrinting},
\citeonline{architectureFormatting},
\citeonline{independentFramework},
\citeonline{industrialApplication},
\citeonline{toolsForProjectManagement},
\citeonline{codeClassification},
\citeonline{codeScanningPatterns},
\citeonline{debuggingIntoExamples},
\citeonline{programUnderstanding},
\citeonline{documentingAndSharingKnowledge},
\citeonline{autofoldingForSourceCode},
\citeonline{learningSupportSystem},
\citeonline{syntaxHighlightingInfluencing},
\citeonline{improvingCodeReadability},
\citeonline{howNovicesRead},
\citeonline{theRoleOfMethodChains},
\citeonline{codeComprehensionComparedToOO},
\citeonline{enhancingLegacySoftwareSystemAnalysis},
\citeonline{moldableCodeEditor},
\citeonline{blindAndSightedProgrammers},
\citeonline{pushdownAutomata},
